The Dynamics of Anthropomorphic Effects in Human-Robot Interaction

### 2014-03-25 paper.tex
Rephrase first section of introduction
Should emphazise the importance of a broader look at anthropomorphism

%{Intro when start with anthropomorphic design}
The Uncanny Valley hypothesis \citep{mori_uncanny_1970} proposes that human-like
designs of objects and non-human agents evoke a positive feeling of affinity in
the human observer / user, which in turn reflects the experience of emotional
engagement with and feelings of empathy for the non-human agent
\citep{cheetham_human_2011}. The positive effect of so-called
\textbf{anthropomorphic form} is exploited in the design of artificial agents
(\eg digital characters, robots) for several reasons. Amongst others,
anthropomorphic design should serve to evoke a positive valence as the Uncanny
Valley hypothesis suggests, which in turn should foster people's acceptance of
the artificial agent, and enable effective (human-like and especially
human-social) interaction.  However, at a certain point as the non-human agent
approaches but fails to closely resemble a human, the evoked valence in the
human user suddenly turns into a negative uncanny feeling of what
\cite{mori_uncanny_1970} describes as disgust and revulsion. This, in turn,
might lead to rejection of the non-human but human-like agent.  The Uncanny
Valley hypothesis predicts that with further increasing the human-likeness of
the non-human agent such that it appears so realistic that it is not
distinguishable from a human but perceived to be human, the effect is again a
positive one, reflecting feelings and engagement that are similar as those
evoked by a human-human interaction.  Of course, roboticists and developers try
to avoid ``falling'' into this Uncanny Valley with their human-like designs of
artificial agents. Consequently, there is a considerable research effort into
better understanding the boundaries of anthropomorphic design and their effect
on the interaction and experience. However, findings have been inconsistent
\citep{cheetham_human_2011}.

A phenomenon that is often studied related to the human-like design of robots is
\textbf{anthropomorphism} (noted \Ant in this paper). Besides a feeling of affinity, and empathy,
anthropomorphism can be understood as being one of the resulting (and  more or
less desired) effects of the anthropomorphic design of artificial agents (up to
the first positive peak). The essence of anthropomorphism is the human user's
perception of human-likeness in the non-human agent. Logically, anthropomorphism
is said to be enhanced with increased human-like design of the agent. There are
various other reasons and explanations for why people tend to anthropomorphize
non-human agents. In general, as anthropomorphism emerges in a (real or
imagined) interaction \citep{persson_anthropomorphism_2000} between at least two
players (the human who anthropomorphizes and the non-human agent which is
anthropomorphized) there are also two main perspectives on the phenomenon: an
artifact-centered (design) and a human-centered (cognitive, psychological) one.
The Uncanny Valley hypothesis can be categorized as being part of first,
artifact-centered approach, to understand anthropomorphism.

>>>>

The Uncanny Valley hypothesis \citep{mori_uncanny_1970} proposes that human-like
designs of objects and non-human agents evoke a positive feeling of affinity in
the human observer / user, which in turn reflects the experience of emotional
engagement with and feelings of empathy for the non-human agent
\citep{cheetham_human_2011}\fxfatal{uncanny valley is not about positive
feeling!}. The positive effect of so-called \textbf{anthropomorphic form} is
exploited in the design of artificial agents
(\eg digital characters, robots) for several reasons. Amongst others,
anthropomorphic design should serve to evoke a positive valence as the Uncanny
Valley hypothesis suggests, which in turn should foster people's acceptance of
the artificial agent, and enable effective (human-like and especially
human-social) interaction.  However, at a certain point as the non-human agent
approaches but fails to closely resemble a human, the evoked valence in the
human user suddenly turns into a negative uncanny feeling of what
\cite{mori_uncanny_1970} describes as disgust and revulsion. This, in turn,
might lead to rejection of the non-human but human-like agent.  The Uncanny
Valley hypothesis predicts that with further increasing the human-likeness of
the non-human agent such that it appears so realistic that it is not
distinguishable from a human but perceived to be human, the effect is again a
positive one, reflecting feelings and engagement that are similar as those
evoked by a human-human interaction.  Of course, roboticists and developers try
to avoid ``falling'' into this Uncanny Valley with their human-like designs of
artificial agents. Consequently, there is a considerable research effort to
better understand the boundaries of anthropomorphic design and their effects
on the interaction and experience. To date, findings have been however
inconsistent \citep{cheetham_human_2011}.

Along this line, this article aims at fostering a better understanding of
anthropomorphism (noted \Ant in this paper) by considering the phenomenon
\textbf{as a whole}: robotics researchers often tend to believe that
anthropomorphism only describes a static set of human-like features of a robot
(like shape, speech capabilities, facial expressions, etc.). We refer to these
characteristics as the \emph{anthropomorphic design} of the
robot~\cite{fink_anthropomorphism_2012}. But \emph{anthropomorphism} in general
refers to the larger \emph{social phenomenon} that emerges from the (real or
imagined) \emph{interaction} between a robot and a
user~\citep{persson_anthropomorphism_2000}. According to~\cite{epley_when_2008},
this includes for instance emotional states, motivations, intentions
\emph{ascribed by the user} to the robot. As such, the dynamic and
socio-cognitive dimensions of anthropomorphism are essential to understand the
complex bonds that human users build with the robots.
